Paper TITLE

### 2016-08-08 paper/Paper.Rmd
Changed LTE in histogram plot

```{r, fig.width=12, fig.height=6, echo = F, message=F,error=F, warning=FALSE}
assisted = clean_years %>% filter(!is.na(assisted)) %>% 
      # Use NSE
      group_by_("assisted", "fmtcostmedrelamicat") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","burden", ",na.rm=T)"))) %>% 
      ungroup %>% 
      mutate(assisted = as.factor(assisted))
ggplot(assisted, aes(y = new_y,   
                  x = fmtcostmedrelamicat,
                  fill = assisted, group = assisted)) +  
  geom_bar(
           stat="identity") + 
  labs(title="Burden based on Median housing cost with assistance",
       y="Burden",
       x = "",
       fill="Assistance") + 
  scale_y_continuous(limits=c(0,1), labels=function(x){paste0(x*100, "%")}) +
  scale_x_discrete(labels = function(x){str_replace_all(x,"^[0-9](.*)","\\1")}) +
  scale_fill_brewer("Assistance", 
                    labels = c("Without Assistance", 
                               "With Assistance"),
                    palette = "Set2")  +
  coord_flip() +
  theme_tufte()
```

>>>>

```{r, fig.width=12, fig.height=6, echo = F, message=F,error=F, warning=FALSE}
assisted = clean_years %>% filter(!is.na(assisted)) %>% 
      # Use NSE
      group_by_("assisted", "fmtcostmedrelamicat") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","burden", ",na.rm=T)"))) %>% 
      ungroup %>% 
      mutate(assisted = as.factor(assisted))
ggplot(assisted, aes(y = new_y,   
                  x = fmtcostmedrelamicat,
                  fill = assisted, group = assisted)) +  
  geom_bar(
           stat="identity") + 
  labs(title="Burden based on Median housing cost with assistance",
       y="Burden",
       x = "",
       fill="Assistance") + 
  scale_y_continuous(limits=c(0,1), labels=function(x){paste0(x*100, "%")}) +
  scale_x_discrete(labels = function(x){str_replace_all(str_replace_all(x, "^[0-9] (.*)","\\1"), "LTE (.*)","<= \\1")}) +
  scale_fill_brewer("Assistance", 
                    labels = c("Without Assistance", 
                               "With Assistance"),
                    palette = "Set2")  +
  coord_flip() +
  theme_tufte()
```
